---
title: "Weight of Fish"
author: "Destiny Calvillo"
date: "Year 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
alldata <- read.csv(file = "Fish.csv")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  


# Perch

```{r}
perch <- filter(alldata, Species == "Perch")
perch <- select(perch,-1)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

library(car)
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The model above is a summary of five different regression models. If we were to find the best regression model that predicts the weight of perch, it appears that we should use the one with two-regressors which is H-W that stands for Height and Width.  

```{r}
which.max(summary.out$adjr2)
```

This summary shows which model is better overall with the best Adjusted R-Squared. 

```{r}
summary.out$which[2,]
```

Both summaries above state that the best model to use that predicts the weight of perch is the regression model that has the two predictor variables Height-Width. 

# Bream

```{r}
bream <- filter(alldata, Species == "Bream")
bream <- select(bream,-1)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = bream,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

library(car)
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The model above is a summary of five different regression models. If we were to find the best regression model that predicts the weight of bream with two variables, it appears that we should use the model that uses L2-H, which stands for Length2 and Height. Though, the one with three-regressors which is L1-H-W that stands for Length1, Height, and Width has a better Adjusted R-Squared. 

```{r}
which.max(summary.out$adjr2)
```

This summary shows which model is better model overall by having the best Adjusted R-Squared, despite the fact that we only want two predictor variables.

```{r}
summary.out$which[2,]
```

The best regression model that predicts the weight of bream by only using two predictor variables is Length2 and Height. The summary above correlates with this conclusion.

# Smelt

```{r}
smelt <- filter(alldata, Species == "Smelt")
smelt <- select(smelt,-1)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = smelt,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

library(car)
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The model above is a summary of five different regression models. If we were to find the best regression model that predicts the weight of smelt by only using two variables, it appears that we should use the model that uses L2-W, which stands for Length2 and Width. Though, the one with four-regressors which is L1-L2-H-W that stands for Length1, Length2, Height, and Width has a better Adjusted R-Squared. 

```{r}
which.max(summary.out$adjr2)
```

This summary shows which model is better model overall by having the best Adjusted R-Squared, despite the fact that we only want two predictor variables.

```{r}
summary.out$which[2,]
```

The summary above correlates with our answer that Length2 and Width are the best two variables to use when predicting the weight of smelt.


